\documentclass[11pt, oneside, a4paper, titlepage]{article}

\usepackage[most]{tcolorbox}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}
\usepackage{array}
\usepackage{geometry}

\geometry{
  a4paper,
  left=0.1cm,
  right=0.1cm,
  top=0.1cm,
  bottom=0.1cm,
}
\newcolumntype{R}{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{7cm}}

\begin{document}

\vspace*{0.2cm}
\hbox{
  \hspace*{0.02\linewidth}
  \begin{minipage}{0.45\linewidth}
    \Huge{Thomas Amighi}
    \vspace*{0.5cm} \\
    \Large{Software developper}
  \end{minipage}%
  \begin{minipage}{0.45\linewidth}
    \begin{flushright}
      \def\arraystretch{1.5}%
      \begin{tabular}[t]{l@{}}
        \textbf{Email}: \href{mailto:thomas.amighi@hotmail.com}{thomas.amighi@hotmail.com} \\
        \textbf{Github}: \url{https://github.com/tamighi} \\
        \textbf{Portfolio}: \url{https://tamighi.github.io}
      \end{tabular}
    \end{flushright}
    \hfill
  \end{minipage}
}

\vspace*{0.5cm}
\begin{tcolorbox}[colframe=white, colback=white]

  \begin{minipage}[t]{0.35\linewidth}

    \section*{Profile}
    I'm a passionate developer looking for
    opportunities to grow. I have 2+ years
    of practical and autonomous experience,
    quickly learning accross different 
    personal projects and thanks to my 
    experience in a fantastic school, 
    the school 42 (I will certainly talk
    a lot about it). \medbreak
    I love to share my knowledge to others 
    and have the opportunity to learn from 
    them. \medbreak
    I am now continuously looking for 
    opportunities to develop my potential, 
    curious of what I will be able to 
    accomplish.

    \section*{Skills}
    \small{
      \textbf{Languages: }Typescript (React, React Native, Angular, NestJS), 
      HTML, CSS, PHP (Symfony), C, C++
    }
    \vspace{0.3cm}
    
    \small{
      \textbf{Database: }SQL, SQLite, Postgres
    }
    \vspace{0.3cm}

    \small{
      \textbf{Tools: }Git, Docker, Jira
    }

    \section*{Hobbies}
    \begin{itemize}
      \item{Music \\(violin, guitar)}
      \item{Sports \\(yoga, running, ...)}
      \item{Learning \\(finances, programming, ...)}
    \end{itemize}

    \section*{Languages}
    \begin{itemize}
      \item{English (Working proficiency)}
      \item{French (Native proficiency)}
    \end{itemize}

  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.60\linewidth}

    \section*{Working Experience}

    \begin{minipage}{0.45\linewidth}
      \textbf{Full stack developer} \\ 
      \textbf{(Angular / Symfony)}
    \end{minipage}
    \begin{minipage}{0.5\linewidth}
      \begin{flushright}
        \underline{aug 2023 - today}
      \end{flushright}
    \end{minipage}
    \vspace{0.3cm}

    \emph{European commission consultant} 
    \vspace{0.3cm}

    \small{
      I worked as an IT consultant in the European Commission's legal 
      service department. I ensured proper migrations and maintenance of Symfony 
      and Angular applications. I built and set up end-to-end tests with Jest, 
      Mocha and WDIO for multiple applications, created a common and reusable 
      library, and wrote complete tests for each client. 
      I developed quality packages (ESLint, Prettier, ...) for frontend and 
      backend applications and utilized Git, Jira, and Bitbucket to deliver the 
      required changes.
    }
    \medbreak

    \section*{Personal Projects 
      \small\normalfont{
        \href{https://tamighi.github.io/}{\underline{(go to portfolio)}}
      }
    }

    \textbf{Correction website} 
    \emph{
      \href{https://tamighi.github.io/work/correction-website-demo}{\underline{go to demo}}
    }
    \medbreak

    \small{
      This full stack website is built using React and NestJS. It is compiled 
      with Webpack, containerized with Docker and optimized with nginx.

      The backend implements an API with authentication, a PostgreSQL database, 
      aswell as a file service and the frontend includes a custom UI library and 
      utilizes React Query for efficient data handling with optimistic and 
      undoable updates.
    }
    \vspace{0.4cm}

    \textbf{Todocal}
    \emph{In progress, see 
      \href{https://github.com/tamighi/todocal}{\underline{github repo}}
    }
    \medbreak

    \small{
      React native expo Calendar application to manage tasks. \\
      I use SQLite and typeorm for the Database and shopify-restyle for the UI.
    }
    \vspace{0.4cm}

    \textbf{Cub3D}
    \emph{
      \href{https://github.com/Lysique/cub3d}{\underline{go to github repo}}
    }
    \medbreak

    This project is inspired from the game Wolfenstein3D, using a rendering 
    technique called the RayCasting. \medbreak

    It is written in C with a simple swift engine. It was coded during my 
    programming studies in school 19, where we could go beyond what was expected.
    \section*{Education}

    \begin{minipage}{0.45\linewidth}
      \textbf{School 19}
    \end{minipage}
    \begin{minipage}{0.5\linewidth}
      \begin{flushright}
        \underline{Aug 2021 - July 2022}
      \end{flushright}
    \end{minipage}
    \vspace{0.4cm}

    \small{
      Deep dive into programmation with C, C++ and Typescript. The school 19 
      (42 network) proposes an interesting way of learning; no teacher, hands 
      on projects and peer to peer evaluation. We construct projects 
      independently and collaboratively with fellow students, and we assess 
      each other's work.
      This was the best way for me to learn programming, allowing me to develop 
      projects autonomously from scratch.
    }
    \vspace{0.2cm}

    \vspace{0.5cm}

    \begin{minipage}{0.45\linewidth}
      \textbf{ULB}
    \end{minipage}
    \begin{minipage}{0.5\linewidth}
      \begin{flushright}
        \underline{Sep 2015 - June 2021}
      \end{flushright}
    \end{minipage}
    \vspace{0.4cm}

    \small{
      Bachelor and master's degree in neuropsychology in the Free University 
      of Brussel. Although I eventually chose a different path, these studies 
      proved valuable through two internships and my thesis. These experiences 
      involved undertaking projects such as implementing a study to analyze the 
      impact of school facilities on children's well-being or investigating 
      abstract letter representation. They also equipped me with skills in data 
      analysis, scientific report writing, and oral presentations.
    }

  \end{minipage}

\end{tcolorbox}

\end{document}
